Accurate binding of sodium and calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-12-19 Manuscript/manuscript.tex
Updated Zenodo references with simulation files ECC-POPC

MD simulations were performed using the GROMACS \cite{Abraham15} simulation package (version 5.1.4). The simulation parameters used
in this work are summarized in Table~S1 in the SI. 
Compatibility with the openMM simulation package \cite{openmm7} was also
tested and is presented in the SI. 
The simulated trajectories and parameters files are available at
Refs.~\citenum{lipid14_POPC_Dang_and_ECC-ions_files, ECC-POPC_nacl_cacl2_files, ECC-POPC_nacl_cacl2_wat-models_files}.
\todo{To be uploaded to Zenodo, references are only placeholders. }.

@@

The cationic surfactants were randomly mixed among the phospholipids to form bilayer structures with mole fractions of 10\%, 20\%, 30\%, 42\%, or 50\% of surfactant in the POPC bilayer. All these systems contained 50 POPC molecules per leaflet, 6340 water molecules, and 6, 14, 21, 35, or 50 surfactants per leaflet.  Chloride counter ions were used in all the simulations, while bromide was the counter ion in the experiment~\cite{scherer89}. For POPC, either Lipid14 with TIP3P~\cite{jorgensen83} or ECC-POPC with SPC/E~\cite{Berendsen1987} parameters  were used. The first 20~ns of the total simulation time of 200~ns was considered as an equilibration period and was thus omitted from the analysis. We checked that a sufficient lipid  exchange occurred during the simulations.
The simulated trajectories and parameters files are available at Ref.~\citenum{ECC-POPC_cationic-surf_files} 
\todo{To be uploaded to Zenodo, references are only placeholders. }.
The trajectories and simulation files for unscaled systems are available at
Refs.~\citenum{POPClipid14T313K,POPClipid1410perCATsurfT313K,POPClipid1420perCATsurfT313K,POPClipid1430perCATsurfT313K,POPClipid1442perCATsurfT313K,POPClipid1450perCATsurfT313K}.

>>>>

MD simulations were performed using the GROMACS \cite{Abraham15} simulation package (version 5.1.4). The simulation parameters used
in this work are summarized in Table~S1 in the SI. 
Compatibility with the openMM simulation package \cite{openmm7} was also
tested and is presented in the SI. 
The simulated trajectories and parameters files are available at
Refs.~\citenum{lipid14_POPC_Dang_and_ECC-ions_files, ECC-POPC_nacl_cacl2_files, ECC-POPC_nacl_cacl2_wat-models_files}.

@@

The cationic surfactants were randomly mixed among the phospholipids to form bilayer structures with mole fractions of 10\%, 20\%, 30\%, 42\%, or 50\% of surfactant in the POPC bilayer. All these systems contained 50 POPC molecules per leaflet, 6340 water molecules, and 6, 14, 21, 35, or 50 surfactants per leaflet.  Chloride counter ions were used in all the simulations, while bromide was the counter ion in the experiment~\cite{scherer89}. For POPC, either Lipid14 with TIP3P~\cite{jorgensen83} or ECC-POPC with SPC/E~\cite{Berendsen1987} parameters  were used. The first 20~ns of the total simulation time of 200~ns was considered as an equilibration period and was thus omitted from the analysis. We checked that a sufficient lipid  exchange occurred during the simulations.
The simulated trajectories and parameters files are available at Ref.~\citenum{ECC-POPC_cationic-surf_files} 
The trajectories and simulation files for unscaled systems are available at
Refs.~\citenum{POPClipid14T313K,POPClipid1410perCATsurfT313K,POPClipid1420perCATsurfT313K,POPClipid1430perCATsurfT313K,POPClipid1442perCATsurfT313K,POPClipid1450perCATsurfT313K}.
